The Talking Heads Experiment

### 2015-04-23 chap11/chap11.tex
changes to headings and minor mistakes across several chapters
hyphenation, punctuation, positioning, etc for chapters 1-6
fix capitalization
hyphenations, footnotes, ...

\chapter{Language strategies for Humanoid Robots}

@@

In January 2007, Luc Steels, Martin Loetzsch, and Michael Spranger traveled to the Sony Computer Science Laboratory 
in Tokyo to do the first experiments with the \textsc{qrio} robots.  
We decided to redo the Talking Heads experiment, but focusing on proper names for individual objects, rather than the emergence 
of generic terms such as colours, shapes or positions.\footnote{The first paper on the Proper Naming Game is: \cite{Steels:2007}
It also discusses the concept of a semiotic network. 
A more recent paper is: \cite{Steels:2012b}. A more 
in-depth discussion of the experiment is included 
in the Ph.D thesis of Martin Loetzsch, defended in 2014 at Humboldt University.}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.85\textwidth]{chap10/figs/png-perception.pdf}}
\caption{\label{fig:png-perception}A robot is looking at consecutive scenes (from top to bottom) and tracking the objects in the scene. One object (labeled $O_{716}$)
is moved by a human experimenter.  We see from left to right: the original source image, results of region detection and 
colour segmentation, the (average) value for one dimension of one object ($O_{716}$), the segmented and labeled objects, 
and the world model, including the position of the other robot (indicated by a pointing arrow). }
\end{figure}

We call the feature vector for each object a {\itshape sensory experience}. \is{sensory experience}
It is represented using a spiking 
diagram, with a spike for each dimension and the value on that dimension marked (see 
\figref{fig:prototypes-identifiers-words}, left-most column). Real
world vision is difficult enough, but because the robots look at the
scene from different points of view, they often do not carve out the
same regions and they will certainly see different views of the
objects and locate them in different positions within their own
egocentric reference frame. So sensory experiences of the same scene
are always going to be different. This makes coordination and hence successful
communication very challenging.

@@

3. The robots need a {\itshape mirror system} that relates perceived actions carried out by others to their own actions. 
The topic of mirror systems has received a lot of attention the past decade because cells were discovered in the brain 
that serve this purpose.\footnote{
An overview of mirror system research and its relevance to the question of the origins of language is given here: 
\cite{Rizzolatti:1998}.}
However the fact that such cells are discovered in the brain 
does not yet tell us how mirror systems are being learned or how they operate. For the action language game, we tried 
several approaches.
\enlargethispage{1\baselineskip}
In one of them, the robot stands before the mirror (\figref{robot-mirror}) and observes its own 
postures, which generates the data for learning the association between body postures and prototypes. 
The robot selects a posture, and activates the corresponding motor behaviour. This motor behaviour generates a sensory image and 
hence a sensory experience categorised with a particular prototype. Through standard Hebbian learning (which enforces the 
connection between nodes that are simultaneously active) the link between the posture prototype and the motor action gets 
established and progressively enforced. 
\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=0.2\linewidth]{chap11/figs/postures.pdf}\includegraphics[width=0.75\linewidth]{chap11/figs/vision_2.pdf}}
\caption{\label{vision}{\itshape Left:} Example postures of the robot (which is the \textsc{qrio} in this case).
{\itshape Right:} Visual analysis. From left to right we see the source image, the foreground/background distinction and object segmentation (focusing on the upper torso), and the feature signature of this posture represented as a graph connecting the values (on the y-axis)
of the seven centralised normalised moments (on the x-axis).}
\end{figure}

@@

\subsection{Compositional Procedural Semantics with IRL}
% {\bfshape Compositional Procedural Semantics with IRL}\\

@@

The basic idea of a constraint language is that only dataflow is expressed explicitly, not control flow. 
There is a set of slots (variables) and a constraint attempts to reduce the set of possible 
fillers (bindings) for a slot. Constraints are combined in 
a constraint network, based on sharing slots. A solution is found when every slot in the network has unique bindings. 
Usually it requires looping several times through the constraints and often even a rewiring of the constraints to 
find a solution. A numerical example of a set of constraints on natural numbers could be:
\begin{verbatim}
  x = y + z with 2<y<5 and 0<x<5
\end{verbatim}
The constraints expressed here form a network because the same variables x and y (which are the slots of the 
network) appear in different constraints (the sum constraint and two instances of the <-constraint). 
Given this network, constraint propagation can compute easily that x = 4, y = 3, and z = 1. 
\enlargethispage{2\baselineskip}
IRL formalises constraints using prefix notation in the following way. Slots are symbols preceded 
by question marks. Constraints are defined with a list with the first argument the name of the constraint and 
the remaining arguments the slots: 
\begin{verbatim}
 (<constraint> <arg1> ... <arg-n>)
\end{verbatim}
The first argument is called the target of the constraint because it is the most logical 'outcome' 
of applying a constraint, but as shown in the example above, data may flow in all directions. The numerical 
example given earlier translates into the following IRL program. 
\begin{verbatim}
(sum ?x ?y ?z)
(between ?y 2 5)
(between ?x 0 5)
\end{verbatim}

@@

\subsection{Building Blocks for Natural Language Semantics}
% {\bfshape Building Blocks for Natural Language Semantics }\\

@@

Let us now look at concrete examples from the colour domain as worked out by Joris Bleys, studying the following 
strategies: \is{colour strategies}
\enlargethispage{1\baselineskip}
1. The first strategy is the {\bfshape Basic Colour Strategy} which implements a prototype-based approach to 
the basic colour categories. This approach is similar to the one used in the Proper Naming Game, except that 
only the three colour-dimensions are profiled (the opponent channels red-green, yellow-blue and the brightness channel). 
The strategy is similar to the one shown earlier. 
\begin{verbatim}
(equal-to-context ?s1) 
(profile-colour-dimensions ?s2 ?s1)
(filter-by-colour-lenient ?s3 ?s2 ?cc)
(select-most-activated ?t ?s3)
\end{verbatim}
When the speaker says `green', this network is used together with a specific binding of ?cc to the prototype for 
green (denoted as [green]). 
\begin{verbatim}
(bind colour-category ?cc [green])
\end{verbatim}
A graphical representation of this network is shown in \figref{fig:basic-strat}.

>>>>

\chapter{Language strategies for humanoid robots}

@@

In January 2007, Luc Steels, Martin Loetzsch, and Michael Spranger traveled to the Sony Computer Science Laboratory 
in Tokyo to do the first experiments with the \textsc{qrio} robots.  
We decided to redo the Talking Heads experiment, but focusing on proper names for individual objects, rather than the emergence 
of generic terms such as colours, shapes or positions.\enlargethispage{1\baselineskip}\footnote{The first paper on the Proper Naming Game is: \cite{Steels:2007}
It also discusses the concept of a semiotic network. 
A more recent paper is: \cite{Steels:2012b}. A more 
in-depth discussion of the experiment is included 
in the Ph.D thesis of Martin Loetzsch, defended in 2014 at Humboldt University.}

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.85\textwidth]{chap10/figs/png-perception.pdf}}
\caption{\label{fig:png-perception}A robot is looking at consecutive scenes (from top to bottom) and tracking the objects in the scene. One object (labeled $O_{716}$)
is moved by a human experimenter.  We see from left to right: the original source image, results of region detection and 
colour segmentation, the (average) value for one dimension of one object ($O_{716}$), the segmented and labeled objects, 
and the world model, including the position of the other robot (indicated by a pointing arrow). }
\end{figure}
\clearpage
We call the feature vector for each object a {\itshape sensory experience}. \is{sensory experience}
It is represented using a spiking 
diagram, with a spike for each dimension and the value on that dimension marked (see 
\figref{fig:prototypes-identifiers-words}, left-most column). Real
world vision is difficult enough, but because the robots look at the
scene from different points of view, they often do not carve out the
same regions and they will certainly see different views of the
objects and locate them in different positions within their own
egocentric reference frame. So sensory experiences of the same scene
are always going to be different. This makes coordination and hence successful
communication very challenging.

@@

3. The robots need a {\itshape mirror system} that relates perceived actions carried out by others to their own actions. 
The topic of mirror systems has received a lot of attention the past decade because cells were discovered in the brain 
that serve this purpose.\footnote{
An overview of mirror system research and its relevance to the question of the origins of language is given here: 
\cite{Rizzolatti:1998}.}
However the fact that such cells are discovered in the brain 
does not yet tell us how mirror systems are being learned or how they operate. For the action language game, we tried 
several approaches.

\enlargethispage{1\baselineskip}
In one of them, the robot stands before the mirror (\figref{robot-mirror}) and observes its own 
postures, which generates the data for learning the association between body postures and prototypes. 
The robot selects a posture, and activates the corresponding motor behaviour. This motor behaviour generates a sensory image and 
hence a sensory experience categorised with a particular prototype. Through standard Hebbian learning (which enforces the 
connection between nodes that are simultaneously active) the link between the posture prototype and the motor action gets 
established and progressively enforced. 
\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=0.2\linewidth]{chap11/figs/postures.pdf}\includegraphics[width=0.75\linewidth]{chap11/figs/vision_2.pdf}}
\caption{\label{vision}{\itshape Left:} Example postures of the robot (which is the \textsc{qrio} in this case).
{\itshape Right:} Visual analysis. From left to right we see the source image, the foreground/background distinction and object segmentation (focusing on the upper torso), and the feature signature of this posture represented as a graph connecting the values (on the y-axis)
of the seven centralised normalised moments (on the x-axis).}
\end{figure}

@@

\subsection{Compositional procedural semantics with IRL}
% {\bfshape Compositional Procedural Semantics with IRL}\\

@@

The basic idea of a constraint language is that only dataflow is expressed explicitly, not control flow. 
There is a set of slots (variables) and a constraint attempts to reduce the set of possible 
fillers (bindings) for a slot. Constraints are combined in 
a constraint network, based on sharing slots. A solution is found when every slot in the network has unique bindings. 
Usually it requires looping several times through the constraints and often even a rewiring of the constraints to 
find a solution. A numerical example of a set of constraints on natural numbers could be:
\begin{verbatim}
  x = y + z with 2<y<5 and 0<x<5
\end{verbatim}
The constraints expressed here form a network because the same variables x and y (which are the slots of the 
network) appear in different constraints (the sum constraint and two instances of the <-constraint). 
Given this network, constraint propagation can compute easily that x = 4, y = 3, and z = 1.

\enlargethispage{2\baselineskip}
IRL formalises constraints using prefix notation in the following way. Slots are symbols preceded 
by question marks. Constraints are defined with a list with the first argument the name of the constraint and 
the remaining arguments the slots: 
\begin{verbatim}
 (<constraint> <arg1> ... <arg-n>)
\end{verbatim}
The first argument is called the target of the constraint because it is the most logical 'outcome' 
of applying a constraint, but as shown in the example above, data may flow in all directions. The numerical 
example given earlier translates into the following IRL program. 
\begin{verbatim}
(sum ?x ?y ?z)
(between ?y 2 5)
(between ?x 0 5)
\end{verbatim}

@@

\subsection{Building blocks for natural language semantics}
% {\bfshape Building Blocks for Natural Language Semantics }\\

@@

Let us now look at concrete examples from the colour domain as worked out by Joris Bleys, studying the following 
strategies: \is{colour strategies}

\enlargethispage{1\baselineskip}
1. The first strategy is the {\bfshape Basic Colour Strategy} which implements a prototype-based approach to 
the basic colour categories. This approach is similar to the one used in the Proper Naming Game, except that 
only the three colour-dimensions are profiled (the opponent channels red-green, yellow-blue and the brightness channel). 
The strategy is similar to the one shown earlier. 
\begin{verbatim}
(equal-to-context ?s1) 
(profile-colour-dimensions ?s2 ?s1)
(filter-by-colour-lenient ?s3 ?s2 ?cc)
(select-most-activated ?t ?s3)
\end{verbatim}
When the speaker says `green', this network is used together with a specific binding of ?cc to the prototype for 
green (denoted as [green]). 
\begin{verbatim}
(bind colour-category ?cc [green])
\end{verbatim}
A graphical representation of this network is shown in \figref{fig:basic-strat}.

### 2015-04-23 chap2/chap2.tex
hyphenations, footnotes, ...

The game is different from a closed world game like 
chess, because the environment is open. The human 
experimenter may introduce new objects at any
time, any one agent can extend
the language (for example invent a new word), possibly
requiring the other agents to adopt it as well, or the
human experimenter may inject new language forms in the 
dialogues. Agents try to maximise their communicative 
success by cooperating to the fullest and update or change
their internal structures and processes
to improve their chances in the game.\footnote{
The Guessing Game is a cooperative game, because
both the agents win or loose at the same time and have 
the highest gain if they develop co-ordinated behaviour. 
The agent who manages to have the most success in the game is 
the global winner. Because the commentator requires to know 
from the speaker which topic he wants to communicate 
before he is allowed to speak, no cheating 
is possible. Game theory, originally founded by John 
von Neumann and Oskar Morgenstern, can be applied to study the 
language game mathematically. \is{game theory} We are dealing with an 
evolutionary game in which the players optimise their 
internal states to become better in the game, see
\cite{Maynard:1982}.}

@@

The environment of the Talking Heads is 
not fixed. The human experimenter 
may change the position of objects, add new kinds of 
objects, or eliminate
others. Consequently a strategy of naming individual objects
will not work. It would lead to a proliferation of 
proper names and it would require the Talking Heads to
recognise objects, which is very difficult to do.\footnote{
For a thorough exposition of the difficulties of 
object recognition, see \cite{Ullman:1996}. 
Object constancy comes fairly late in the 
acquisition of a child's ontology, as Piaget's conservation
experiments have shown. Language probably plays an important
role in forming the notion of an object.}
Indeed, humans don't exclusively use proper names in 
natural language conversations 
either. We say `could you give me the red small square' as 
opposed to `could you give me O\_143'. Natural language
words like `red' or `small' name perceptually grounded categories
and syntactic structures indicate how they should
be combined and used to find the topic. The relation between 
a language expression and its referent is therefore 
always indirect. This is summarised
in the semiotic square (\figref{triangle}), which I will use throughout this book to 
help understand and analyse the nature of language communication. \is{semiotic square}
The semiotic square relates the four entities
involved in a verbal interaction: 
\begin{itemize}
\item An {\itshape utterance}, such as `small red square', which is 
transmitted as a physical 
signal from one agent to another one through the 
external environment. It is written between double quotes. 
\item A {\itshape meaning}, which consists of categories like [\textsc{red}], [\textsc{small}], 
or combinations of categories, like \{[\textsc{red}] [\textsc{small}]\}. Labels of 
categories are written in capital letters between 
square brackets. 
\item An {\itshape image segment}, denoted as \emph{S143}, which is 
a segment of the image perceived through the camera.
\item A {\itshape referent}, like object \emph{O143}, which is 
an entity in the real world. 
\end{itemize}

>>>>

The game is different from a closed world game like 
chess, because the environment is open. The human 
experimenter may introduce new objects at any
time, any one agent can extend
the language (for example invent a new word), possibly
requiring the other agents to adopt it as well, or the
human experimenter may inject new language forms in the 
dialogues. Agents try to maximise their communicative 
success by cooperating to the fullest and update or change
their internal structures and processes \enlargethispage{1\baselineskip}
to improve their chances in the game.\footnote{
The Guessing Game is a cooperative game, because
both the agents win or loose at the same time and have 
the highest gain if they develop co-ordinated behaviour. 
The agent who manages to have the most success in the game is 
the global winner. Because the commentator requires to know 
from the speaker which topic he wants to communicate 
before he is allowed to speak, no cheating 
is possible. Game theory, originally founded by John 
von Neumann and Oskar Morgenstern, can be applied to study the 
language game mathematically. \is{game theory} We are dealing with an 
evolutionary game in which the players optimise their 
internal states to become better in the game, see
\cite{Maynard:1982}.}

@@

The environment of the Talking Heads is 
not fixed. The human experimenter 
may change the position of objects, add new kinds of 
objects, or eliminate
others. Consequently a strategy of naming individual objects
will not work. It would lead to a proliferation of 
proper names and it would require the Talking Heads to
recognise objects, which is very difficult to do.\footnote{
For a thorough exposition of the difficulties of 
object recognition, see \cite{Ullman:1996}. 
Object constancy comes fairly late in the 
acquisition of a child's ontology, as Piaget's conservation
experiments have shown. Language probably plays an important
role in forming the notion of an object.}
Indeed, humans don't exclusively use proper names in 
natural language conversations 
either. We say `could you give me the red small square' as 
opposed to `could you give me O\_143'. Natural language
words like `red' or `small' name perceptually grounded categories
and syntactic structures indicate how they should
be combined and used to find the topic. The relation between 
a language expression and its referent is therefore 
always indirect. This is summarised
in the semiotic square (\figref{triangle}), which I will use throughout this book to 
help understand and analyse the nature of language communication. \is{semiotic square}
The semiotic square relates the four entities
involved in a verbal interaction: 
\begin{itemize}
\item An {\itshape utterance}, such as `small red square', which is 
transmitted as a physical 
signal from one agent to another one through the 
external environment. It is written between double quotes. 
\item A {\itshape meaning}, which consists of categories like [\textsc{red}], [\textsc{small}], 
or combinations of categories, like \{[\textsc{red}] [\textsc{small}]\}. Labels of 
categories are written in capital letters between 
square brackets. 
\clearpage
\item An {\itshape image segment}, denoted as \emph{S143}, which is 
a segment of the image perceived through the camera.
\item A {\itshape referent}, like object \emph{O143}, which is 
an entity in the real world. 
\end{itemize}

### 2015-04-23 chap3/chap3.tex
hyphenations, footnotes, ...

Working \todo{3.5.1 cannot remain the only subsection of 3.5} with simulations has obvious advantages for 
speeding up development and systematic testing, 
but it does not replace experimentation with 
physical robots. It is true that 
building an experimental apparatus such as we built
for the Talking Heads experiment is a very 
non-trivial engineering project, particularly because 
of the teleporting infrastructure that enables the agents 
to travel to multiple sites and thus 
experience different physical environments or the same 
environment from different points of view. 
One might therefore wonder why we have persisted
to go to such great length in constructing
a real-world physical infrastructure. Why are
experiments with robotic agents necessary or 
desirable? Is it not enough to conduct simulation
experiments given that they can be done so much 
more easily?

>>>>

Working \todo{3.5.1 is orphaned} with simulations has obvious advantages for 
speeding up development and systematic testing, 
but it does not replace experimentation with 
physical robots. It is true that 
building an experimental apparatus such as we built
for the Talking Heads experiment is a very 
non-trivial engineering project, particularly because 
of the teleporting infrastructure that enables the agents 
to travel to multiple sites and thus 
experience different physical environments or the same 
environment from different points of view. 
One might therefore wonder why we have persisted
to go to such great length in constructing
a real-world physical infrastructure. Why are
experiments with robotic agents necessary or 
desirable? Is it not enough to conduct simulation
experiments given that they can be done so much 
more easily?

### 2015-04-23 chap5/chap5.tex
hyphenations, footnotes, ...

The \todo{This intro is too long} semiotic square captures the four entities in 
a linguistic interaction: 
the {\itshape referent}, which is the object in the physical world that the 
speaker wants to communicate, the {\itshape segmented image}, which is 
the internal perception of the referent, the {\itshape meaning}, which is a 
category or combination of categories that picks out the 
referent in the present context, and 
the {\itshape utterance}, which is the word form 
or set of word forms transmitted by the speaker. In the previous 
chapters we looked at two sides of the semiotic
square. The relation between the real world and the
perceived image was studied in chapter 3 and the relation
between the perceived image and a conceptualisation that 
could act as the meaning for a language communication was 
studied in chapter 4. We now turn to the next side of 
the semiotic square: the relation between meaning and 
utterance.

@@

The following vocabularies illustrate this point clearly.
The first vocabulary is taken from an agent from the
leftmost cluster in \figref{figure-agent-distribution}. 
All the words associated with a particular meaning are 
shown together with their score. \todo{What do the \{ and \} mean?}
\begin{verbatim}
{}[M0]: kube[0.88] gutida[0.00] moko[0.00]
{}[M1]: nugini[0.97] gi[0.83] majiba[0.00]
{}[M2]: go[0.98] ta[0.00]
{}[M3]: moma[0.98] ti[0.00] nudo[0.00] kene[0.00]
{}[M4]: nebu[0.98] me[0.83]
{}[M5]: tine[0.98]
\end{verbatim}
\begin{verbatim}
{}[M6]: bo[0.94] babige[0.82]
{}[M7]: mepabo[0.97] jabeto[0.71] di[0.00]
{}[M8]: kude[0.90] nado[0.00]
{}[M9]: pe[0.94] da[0.00]
{}[M10]: na[0.94] nuguge[0.90] pa[0.80] ne[0.00]
\end{verbatim}
\begin{verbatim}
{}[M11]: mu[0.98] gite[0.00] paku[0.00]
{}[M12]: gema[0.96] do[0.33] gapu[0.00]
{}[M13]: ja[0.67] jo[0.00]
{}[M14]: dodine[0.88] pibo[0.83] gije[0.00] pupeto[0.00]
{}[M15]: jiti[0.94] gato[0.64]
\end{verbatim}
\begin{verbatim}
{}[M16]: bimogu[0.98] ba[0.00]
{}[M17]: bapi[0.96] ki[0.81] damuti[1,0,0.00]
{}[M18]: kutume [0.94] bu [0.00] ni[0.00]
{}[M19]: mugu[0.95] NINU[0.50] pi[0.43] ji[0.00] tu[0.00]
\end{verbatim}
This is the vocabulary for an agent taken from the
rightmost cluster in \figref{figure-agent-distribution}:
\begin{verbatim}
{}[M0]: gutida[0.79] kube[0.00]
{}[M1]: gi[0.89] matu[0.85] pumoni[0.00]
{}[M2]: go[0.95] ta[0.20]
{}[M3]: kene[0.89] moma[0.82] nudo[0.00] koko[0.00]
{}[M4]: nebu[0.97] me[0.00] bukugo[0.00]
{}[M5]: tine[0.90]
\end{verbatim}
\begin{verbatim}
{}[M6]: babige[0.93] bo[0.00]
{}[M7]: mepabo[0.90] junipe[0.75] di[0.00]
{}[M8]: nado[0.96] kude[0.80] puto[0.00]
{}[M9]: da[0.86] nine[0.71]
{}[M10]: pa[0.87]
\end{verbatim}
\begin{verbatim}
{}[M11]: gite[0.88]
{}[M12]: gema[0.90] gapu[0.87]
{}[M13]: jo[0.96] ji[0.89] ja[0.00]
{}[M14]: dodine[0.96] pupeto[0.56] pibo[0.00] gije[0.00]
{}[M15]: jiti[0.97] gato[0.46]
\end{verbatim}
\begin{verbatim}
{}[M16]: bimogu[0.97] ba[0.83] pipebe[0.00]
{}[M17]: ki[0.97] bapi[0.00] ke[,0.00]
{}[M18]: ni[0.94] kutume[0.80] moko[0.80] mekami[0.00]
{}[M19]: ninu[0.81] mugu[0.00] pi[0.00]
\end{verbatim}
Some words (for example `tine' for [M5] or `go' for [M2]) are
shared. But generally 
there are at least two words. One word is used preferentially inside the cluster,
the other is known but preferentially used by members of another cluster. Thus
the word `mugu' for [M19] is preferred for the first object in the first
cluster and known but not preferentially used by the agent in the second cluster.
Conversely, `ninu' is preferred for the same meaning by the agent in the second
cluster, although he also knows `mugu'.
`mepabo' for [M7] belongs to the interlingua. Both agents
know and use it but they have a strong alternative `jabeto' for 
the first and `junipe' for the second agent.

>>>>

The semiotic square captures the four entities in 
a linguistic interaction: 
the {\itshape referent}, which is the object in the physical world that the 
speaker wants to communicate, the {\itshape segmented image}, which is 
the internal perception of the referent, the {\itshape meaning}, which is a 
category or combination of categories that picks out the 
referent in the present context, and 
the {\itshape utterance}, which is the word form 
or set of word forms transmitted by the speaker. In the previous 
chapters we looked at two sides of the semiotic
square. The relation between the real world and the
perceived image was studied in chapter 3 and the relation
between the perceived image and a conceptualisation that 
could act as the meaning for a language communication was 
studied in chapter 4. We now turn to the next side of 
the semiotic square: the relation between meaning and 
utterance.

@@

The following vocabularies illustrate this point clearly.
The first vocabulary is taken from an agent from the
leftmost cluster in \figref{figure-agent-distribution}. 
All the words associated with a particular meaning are 
shown together with their score.
\begin{verbatim}
{}[M0]: kube[0.88] gutida[0.00] moko[0.00]
{}[M1]: nugini[0.97] gi[0.83] majiba[0.00]
{}[M2]: go[0.98] ta[0.00]
{}[M3]: moma[0.98] ti[0.00] nudo[0.00] kene[0.00]
{}[M4]: nebu[0.98] me[0.83]
{}[M5]: tine[0.98]
\end{verbatim}
\begin{verbatim}
{}[M6]: bo[0.94] babige[0.82]
{}[M7]: mepabo[0.97] jabeto[0.71] di[0.00]
{}[M8]: kude[0.90] nado[0.00]
{}[M9]: pe[0.94] da[0.00]
{}[M10]: na[0.94] nuguge[0.90] pa[0.80] ne[0.00]
\end{verbatim}
\begin{verbatim}
{}[M11]: mu[0.98] gite[0.00] paku[0.00]
{}[M12]: gema[0.96] do[0.33] gapu[0.00]
{}[M13]: ja[0.67] jo[0.00]
{}[M14]: dodine[0.88] pibo[0.83] gije[0.00] pupeto[0.00]
{}[M15]: jiti[0.94] gato[0.64]
\end{verbatim}
\begin{verbatim}
{}[M16]: bimogu[0.98] ba[0.00]
{}[M17]: bapi[0.96] ki[0.81] damuti[1,0,0.00]
{}[M18]: kutume [0.94] bu [0.00] ni[0.00]
{}[M19]: mugu[0.95] NINU[0.50] pi[0.43] ji[0.00] tu[0.00]
\end{verbatim}
This is the vocabulary for an agent taken from the
rightmost cluster in \figref{figure-agent-distribution}:
\begin{verbatim}
{}[M0]: gutida[0.79] kube[0.00]
{}[M1]: gi[0.89] matu[0.85] pumoni[0.00]
{}[M2]: go[0.95] ta[0.20]
{}[M3]: kene[0.89] moma[0.82] nudo[0.00] koko[0.00]
{}[M4]: nebu[0.97] me[0.00] bukugo[0.00]
{}[M5]: tine[0.90]
\end{verbatim}
\begin{verbatim}
{}[M6]: babige[0.93] bo[0.00]
{}[M7]: mepabo[0.90] junipe[0.75] di[0.00]
{}[M8]: nado[0.96] kude[0.80] puto[0.00]
{}[M9]: da[0.86] nine[0.71]
{}[M10]: pa[0.87]
\end{verbatim}
\begin{verbatim}
{}[M11]: gite[0.88]
{}[M12]: gema[0.90] gapu[0.87]
{}[M13]: jo[0.96] ji[0.89] ja[0.00]
{}[M14]: dodine[0.96] pupeto[0.56] pibo[0.00] gije[0.00]
{}[M15]: jiti[0.97] gato[0.46]
\end{verbatim}
\begin{verbatim}
{}[M16]: bimogu[0.97] ba[0.83] pipebe[0.00]
{}[M17]: ki[0.97] bapi[0.00] ke[,0.00]
{}[M18]: ni[0.94] kutume[0.80] moko[0.80] mekami[0.00]
{}[M19]: ninu[0.81] mugu[0.00] pi[0.00]
\end{verbatim}
Some words (for example `tine' for [M5] or `go' for [M2]) are
shared. But generally 
there are at least two words. One word is used preferentially inside the cluster,
the other is known but preferentially used by members of another cluster. Thus
the word `mugu' for [M19] is preferred for the first object in the first
cluster and known but not preferentially used by the agent in the second cluster.
Conversely, `ninu' is preferred for the same meaning by the agent in the second
cluster, although he also knows `mugu'.
`mepabo' for [M7] belongs to the interlingua. Both agents
know and use it but they have a strong alternative `jabeto' for 
the first and `junipe' for the second agent.
